Programming Assignment 2

### 2015-04-02 paper.tex
Began working on the Project Report (BAM)
Worked on documenting BAM in the paper

\subsection{Image Encoding}
All images being imported into BAM are required to be in a JPG format. These
images are then imported, resized into a standard format, and then polarized.
Each polarized image is then translated into a single dimensional vector.
Each 'class' of images are grouped together column wise to create a centroid
matrix.

\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

It seems that the BAM implementation attempted to classify nearly all animals
as dogs. For planes the network had more diverse attempts to classify each
object, although incorrectly. The marine results showed the most diverse and
correct classifications. Although it does seem that BAM attempted to describe
everything as either a submarine or a whale.
\subsection{Sensitivity}
This section is about how badly noise and the size disrupted our accuracy

@@

\subsubsection{Project Presentation}
NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER

\subsection{Skyler Manzanares}

>>>>

\subsection{Encoding}
\subsubsection{Images}
All images being imported into BAM are required to be in a JPG format. These
images are then imported, resized into a standard format, and then polarized.
Each polarized image is then translated into a single dimensional vector.
Each 'class' of images are grouped together column wise to create a centroid
matrix.

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6.
Each class 'supersection' had a total of 3 classes. The animal supersection
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
and Whales. Each supersection is treated separately. The encodings for Animals
are used again in Planes and Marines. This was to make the classification
encodings as simple yet distant as possible.
\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

It seems that the BAM implementation attempted to classify nearly all animals
as dogs. For planes the network had more diverse attempts to classify each
object, although incorrectly. The marine results showed the most diverse and
correct classifications. Although it does seem that BAM attempted to describe
everything as either a submarine or a whale.

\subsection{Sensitivity}
Noise significantly disrupted the creation of the centroids in our Project.
As a result we removed all excessive details and attempted to leave just
the pure outlines. Of course this also may have made our centroid to being
too sanitied and noisy images would be more likely to be misclassified.

\subsection{Comments}
BAM performed rather poorly. It appeared that BAM favored a single class when
attempting to classify. However I believe this is a result of our encoding 
scheme. If we had made our own outlines our network could have performed 
better. Larger sizes could also give some accuracy in exchange for computational
power.

@@

\subsubsection{Project Presentation}
NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER
SKYLER, SKYYYYLLLLEERRRRR, SKYLLLLERRR NOOOOOOOOOOOOOOOOOOOOO
\subsection{Skyler Manzanares}
